Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-11 size_differentiated_export.tex

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%
\begin{abstract}
% Mat: I think that even with the submesoscale mechanism, export is mainly driven by gravitational sinking. So I'm moving the "Traditionally" to later. 
Export of particulate organic carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles. Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the particle number size-spectrum slope, and (2) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles in POC export. A steeper particle size spectrum, also increases the contribution of smaller, slower-sinking particles. Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles are significant contribution, and at times, can even dominate the export flux. 
\end{abstract}

@@

The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities. Considering the fact that, although containing less biomass, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant. Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ. Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and are more often than not inferred from key parameters such as particle type, size, and density.

@@

Time-varying wind stress and heat flux are prescribed at the surface boundary. Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory\footnote{https://www.pmel.noaa.gov/ocs/Papa}. Climatologies of daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long time series. A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability. In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing apply at the surface boundary. Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10. % (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling that could contaminate the middle third of the model domain, where the analysis is focused (Figure \ref{fig: model_domain}a). A restoration time scale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b). Net surface heat fluxes are homogeneously prescribed throughout the domain, over which a linear meridional heat flux anomaly is superimposed to maintain a north-south gradient (Figure \ref{fig: model_domain}c). The flux anomaly is zero in the center of the domain, associated with the latitude of Station Papa, and has a meridional slope of 1/24 W/m$^2$/km, which was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}.

Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from ARGO floats \citep{Gaillard_2009,Gaillard_2016}. ARGO data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}). The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}). The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}. To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength close to the 1st baroclinic deformation radius ($\lambda = $ 66 km). Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role. Submesoscale dynamics are characterized by sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km). Such dynamics are more likely to be found in the winter time, where mixed layers are deeper and lateral density gradients enhanced \citep{Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

In \textit{Papa\_summer}, PSOM is initialized based on climatological ARGO data in April. The magnitude of the density gradient across the front (i.e., frontal sharpness) is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}). The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing summer stratification to develop. The model is then run for 30 additional days, saving instantaneous model fields every 3 hours for particle tracking. The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}). In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.

%TAB1
\begin{table}[t]
\caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
	\label{tab: meso_vs_submeso}
	\centering
 \centering
\begin{tabular}{|l|c|c|}
		\hline
											& \textit{Papa\_summer} & \textit{Papa\_winter} \\
		\hline
		Time period 								& April -- July             & January -- March          \\
		Spin-up								        & 60 days                   & 50 days                   \\
		Advective timestep				            & 216 s                     & 108 s                     \\
		Horizontal diffusivity			            & 1 m$^2$ s$^{-1}$          & 0.2 m$^2$ s$^{-1}$        \\
		Restoration timescale			            & 3 days                    & 15 days                   \\
		Maximum initial M$^2$ ($\times$10$^{-8}$)	& 3.2 s$^{-2}$             & 33.9 s$^{-2}$             \\	
		Maximum initial N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
		Initial mixed layer depth                   & 73 m                      & 85 m                      \\
		Zonal wind stress                	        & 0 -- 0.16 N m$^{-2}$      & -0.05 -- 0.17 N m$^{-2}$  \\	
		Surface heat flux               	        & -46.8 -- 167.5 W m$^{-2}$ & -57.6 -- 15.3 W m$^{-2}$  \\	
		\hline
	\end{tabular}
\end{table}

@@

% FIG2
\begin{figure}[t]
	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
	\caption{PSOM configuration for \textit{Papa\_summer}. (a) Time series of net heat fluxes and wind stress prescribed at the surface. Notice the positive heat fluxes, as well as downfront winds (i.e. eastward) persisting throughout the experiment. (b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_summer}
\end{figure}

@@

In \textit{Papa\_winter}, PSOM is initialized based on climatological ARGO data in January. The frontal sharpness is set to 3.54$\times$10$^{-5}$ kg/m$^3$/m, which corresponds to the 99$^{th}$ percentile of the PDF of density gradients measured in January from glider data collected in the region (Figure \ref{fig: Papa_winter} and Table \ref{tab: meso_vs_submeso}). The model is allowed to spin-up for 50 days allowing for the prescribed fronts to become unstable. To accommodate the larger density gradients, the advective timestep is shortened to 108 s, and the horizontal diffusivity is lowered to 0.2 m$^2$/s. The model is run for 30 additional days, saving instantaneous model fields every 1.5 hours for particle tracking. The month of January is chosen for initialization so the experiment would capture the time of year where the mixed layer is the deepest, and Rossby number of O(1) are more likely to occur. The objective is for this experiment to contrast \textit{Papa\_summer} by capturing the statistics of ocean conditions dominated by submesoscale dynamics.

@@

To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.
During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa. Gliders sample the water column in a triangular wave pattern, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr). It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time. To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie. Each along-track buoyancy gradient is thus associated with a specific separation scale and a timestamp. Glider-based density gradients can be affected by internal waves. To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of twice the Rossby radius $\pm$ 1 km are considered. Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.

@@

The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

@@

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400$\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}. \cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size. Assuming a Stokes-like relationship, (\ref{eq: powerlaw_radius}) can be re-written in terms of sinking velocities as:

\begin{equation}
N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
\label{eq: powerlaw_velocity}
\end{equation}
For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to vary with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

\begin{equation}
	B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
	\label{eq: biomass_realparticle}
\end{equation}
where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

\subsubsection{Particle Remineralization Scheme}
\label{sec: remin_scheme}
Remineralization of particles as they sink through the water column evidently impacts the export of biomass. Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles. In this study, the impact of remineralization is considered through the implementation of a time-dependent sinking velocity. Remineralization processes driving remineralization rates are complex, species-dependent, and generally not well-understood. In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time. This implicitly assumes that the biomass content of a particle decreases in time proportionally to the particle volume. Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
\begin{equation}
	B (t) = B^0\exp(-kt)
	\label{eq: remin_scheme}
\end{equation}
where $B^0$ denotes the biomass content at $t = 0$ days, and $k = 0.13$ day$^{-1}$. This remineralization rate determined by \cite{Iversen_2010} is independent of particle sinking velocity, and seems to generally agree with other findings, despite the large uncertainties \citep{Ploug_2008, Iversen_2013}. The change in biomass with time is in turn expected to affect the sinking velocity of the particle. Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to:

>>>>

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%
\begin{abstract}
% Mat: I think that even with the submesoscale mechanism, export is mainly driven by gravitational sinking. So I'm moving the "Traditionally" to later. 
Export of particulate organic carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles. Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export. A steeper particle size spectrum, also increases the contribution of smaller, slower-sinking particles. Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux. 
\end{abstract}

@@

The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities. Considering the fact that, although containing less biomass per particle, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant. Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ. Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and are more often than not inferred from key parameters such as particle type, size, and density.

@@

Time-varying wind stress and heat flux are prescribed at the surface boundary. Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory. Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology. A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability. In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing applied at the surface boundary. Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10. % (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling %that could contaminate the middle third of the model domain, where the analysis is focused 
(Figure \ref{fig: model_domain}a). A restoration timescale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b). While net surface heat fluxes are homogeneous in the zonal direction, a meridional gradient is maintained throughout the simulation. The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).

Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \citep{Gaillard_2009,Gaillard_2016}. Argo data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}). The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}). The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}. To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength close to the 1st baroclinic deformation radius ($\lambda = $ 66 km). Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

In \textit{Papa\_summer}, PSOM is initialized based on climatological Argo data in April. The magnitude of the density gradient across the front is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}). The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing summer stratification to develop. The model is then run for 30 additional days, saving instantaneous model fields every 3 hours for particle tracking. The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}). In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pellets, dead phytoplankter; ][]{Plant_2016}.

%TAB1
\begin{table}[t]
\caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
	\label{tab: meso_vs_submeso}
	\centering
 \centering
\begin{tabular}{|l|c|c|}
		\hline
											& \textit{Papa\_summer} & \textit{Papa\_winter} \\
		\hline
		Time period 								& April -- July             & January -- March          \\
		Spin-up								        & 60 days                   & 50 days                   \\
		Advective timestep				            & 216 s                     & 108 s                     \\
		Horizontal diffusivity			            & 1 m$^2$ s$^{-1}$          & 0.2 m$^2$ s$^{-1}$        \\
		Restoration timescale			            & 3 days                    & 15 days                   \\
		Zonal wind stress                	        & 0 -- +0.16 N m$^{-2}$      & -0.05 -- +0.17 N m$^{-2}$  \\	
		Surface heat flux               	        & -46.8 -- +167.5 W m$^{-2}$ & -57.6 -- +15.3 W m$^{-2}$  \\
		Maximum M$^2$ ($\times$10$^{-8}$)	        &                           &                           \\[-.25cm]
		\multicolumn{1}{|r|}{initial}	            & 3.2 s$^{-2}$              & 33.9 s$^{-2}$             \\[-.25cm]
		\multicolumn{1}{|r|}{spun-up}	            & 12.0 s$^{-2}$             & 50.0 s$^{-2}$             \\	
		Maximum N$^2$ ($\times$10$^{-4}$)	        &                           &                           \\[-.25cm]
		\multicolumn{1}{|r|}{initial}	            & 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\[-.25cm]
		\multicolumn{1}{|r|}{spun-up}	            & 3.1 s$^{-2}$              & 1.1 s$^{-2}$              \\	
		Averaged mixed layer depth                  &                           &                           \\[-.25cm]
		\multicolumn{1}{|r|}{initial}	            & 73 m                      & 85 m                      \\[-.25cm]
		\multicolumn{1}{|r|}{spun-up}	            & 11 m                      & 93 m                      \\	
		\hline
	\end{tabular}
\end{table}

@@

% FIG2
\begin{figure}[t]
	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
	\caption{PSOM configuration for \textit{Papa\_summer}. (a) Time series of net heat fluxes and wind stress prescribed at the surface. Notice the positive heat fluxes, as well as downfront winds (i.e. eastward) persisting throughout the experiment. (b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at day of year 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_summer}
\end{figure}

@@

In \textit{Papa\_winter}, PSOM is initialized based on climatological Argo data in January. The frontal gradient is set to 3.54$\times$10$^{-5}$ kg/m$^3$/m, which corresponds to the 99$^{th}$ percentile of the PDF of density gradients measured in January from glider data collected in the region (Figure \ref{fig: Papa_winter} and Table \ref{tab: meso_vs_submeso}). The model is allowed to spin-up for 50 days allowing for the prescribed fronts to become unstable. To accommodate for the larger density gradients and stronger velocities, the advective timestep is shortened to 108 s and the horizontal diffusivity is lowered to 0.2 m$^2$/s throughout the experiment. The model is run for 30 additional days, saving instantaneous model fields every 1.5 hours for particle tracking. The month of January is chosen for initialization so the experiment would capture the time of year where the mixed layer is the deepest, and Rossby number O(1) occur more frequently. The objective is for this experiment to contrast \textit{Papa\_summer} by capturing the statistics of ocean conditions dominated by submesoscale dynamics.

@@

To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.
During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa. Gliders sample the water column in a triangular wave pattern, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr). It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time. To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie. Each along-track lateral buoyancy gradient is thus associated with a specific separation scale and a timestamp. Glider-based density gradients can be affected by internal waves. To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of twice the Rossby radius $\pm$ 1 km are considered. Rossby radii are estimated from the glider data and are $\sim8$ km in winter and $\sim20$ km in summer.

@@

The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

@@

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically. Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}. %\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size. 
Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), where $w_{s_0}$ is the sinking speed of particles with a radius $r_0$:

\begin{equation}
N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
\label{eq: powerlaw_velocity}
\end{equation}
For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to scale with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Number of particles (solid) and biomass (dashed) normalized to the fastest-sinking particle class as a function of sinking velocity $w_s$. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

\begin{equation}
	B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
	\label{eq: biomass_realparticle}
\end{equation}
where $B_p(w_{s_0})$ is the biomass of a particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

\subsubsection{Particle Remineralization Scheme}
\label{sec: remin_scheme}
Remineralization of particles as they sink through the water column impacts the amount of biomass exported. Slow-sinking particles generally contains less biomass and spends more time in the mixed layer, which means that they are remineralized at a shallower depth than faster sinking particles. Remineralization processes are complex, species-dependent, and generally not well-understood. In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship which assumes that the biomass content of a particle decreases in time proportionally to the particle volume. Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
\begin{equation}
	B (t) = B^0\exp(-kt)
	\label{eq: remin_scheme}
\end{equation}
where $B^0$ denotes the biomass content at $t = 0$ days, and the remineralization rate is taken to be $k = 0.13$ day$^{-1}$ in this study \citep{Iversen_2010}. This remineralization rate is independent of particle sinking velocity, and seems to lie within the range of other estimates \citep{Ploug_2008, Iversen_2010, Iversen_2013}. The change in biomass with time is in turn expected to affect the sinking velocity of the particle. Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to:
